An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-10-31 appendix.tex

\newcommand{\WesA}[1][]{\oclt{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1} F_t^{#1} \osum{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\oclt{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}

@@

\noindent%
This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test of equal
predictive accuracy for nested models.''
Define the additional notation
$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
$F_t = F_t(\btrue)$,
and
$h_t = h_t(\btrue)$.

\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
\begin{proof}
  Replace $R$ with $\log(T)$ and $P$ with $T - \log(T)$ in the
  statistic; this substitution does not affect its asymptotic
  distribution.
  As in \citet{Wes:96} and \citet{WeM:98}, expand $\fh_t$ around
  $\btrue$ to get
  \begin{align*}
    \sqrt{P} \big(\fb - \fb(\btrue)\big) &= \oclt{t}
    \big(f_t - \E f_t\big) +
    \E F_t B \oclt{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t
  \end{align*}
  where (again, as in \citealp{Wes:96}) the $i$th element of $w_t$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\bh_t - \btrue)'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'}
    f_{it}(\bt_{it}) \Big]
    (\bh_t - \btrue)
  \end{equation*}
  and each $\bt_{it}$ lies between $\bh_t$ and
  $\btrue$; $\oclt{t} w_t = o_{p}(1)$ as in Theorem~\ref{res:3}.
  Then, as before,
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12}\\
  \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  from Lemma~\ref{res:a4}.  The formula of the asymptotic variance can
  be derived exactly as in \citet{Wes:96} and \citet{WeM:98}.

  Note that \[f_t(\btrue)= 2 (y_{t+1} -
  x_t'\btrue)(\yh_{1,t+1} - x_t'\btrue) \quad \text{a.s.},\] as
  in \citet{ClW:07}, which is an \mds, so we do not need to use a
  \hac\ estimator of the variance under the null.  Also observe that
  \[F_t(\beta) = 2 x_t(x_t'\beta - \yh_{1,t+1}) + 2 x_t(x_t'\beta -
  y_{t+1})\] and the second term is an \mds\ under the null,
  explaining the particular form of $g_t(\beta)$.
\end{proof}

@@

\begin{alem}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$.
  \item $P^a \sup_t | \bh_{t} - \btrue | \to^{p} 0$.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t) = O_{p}(1)$.
  \end{enumerate}
\end{alem}

\begin{proof}
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies
    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.
  \item We have
    \begin{equation}
      P^a \sup_t | \bh_t - \btrue | = P^a \sup_t |\Bh_{t}
      H_{t}| \leq \sup_{t,u} \Big| [ \Bh_u - B]
      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{equation}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T (F_t - \E F_t)$ obeys
    \citepos{Jon:97} \clt, so the result is trivial.
  \end{enumerate}
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{res:a4}]
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lvert \oclt{t} (F_t - \E F_t) B \Big\rvert
  \sup_t | H_t |.
\end{equation*}
From Lemma~\ref{res:a2}, $\sup_t | H_t | \to^p 0$ and $\oclt{t}
(F_t - \E F_t) = O_p(1)$, establishing~\eqref{eq:11}. The proofs
of \eqref{eq:12} and \eqref{eq:13} are similar.
\end{proof}

>>>>

\newcommand{\WesA}[1][]{\ocltb{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} \E^{#1}(F_t^{#1}) \osumb{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\ocltb{t}
  (F_t^{#1} - \E^{#1} F_t^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}

@@

\noindent%
This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test of equal
predictive accuracy for nested models.''
Define the additional notation 
$f_t = f_t(\btrue)$,
$F_t(\beta) = \tfrac{\partial}{\partial \beta} f_t(\beta)$,
$F_t = F_t(\btrue)$,
$h_t = h_t(\btrue)$,
and
\begin{equation*}
  H_{t} = \tfrac1t \sum_{s=1}^t h_{s}.
\end{equation*}
All of the proofs in this section will be presented for the case where
there is a single alternative model. The Cram\'er-Wold device ensures
that the corresponding multivariate results follow trivially.

\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
\begin{proof}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation*}
    \sqrt{P} (\fb - \E \fb(\btrue))
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^{R'} (\fh_t - \E f_t).
  \end{equation*}
  Lemma~\ref{res:a1} ensures that the second term is $o_p(1)$, and
  we can rewrite this summation as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb(\btrue))
    &= \ocltb{t} (f_t - \E f_t) + \E(F_t) B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.

  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. Finally,
  \begin{equation*}
    \oclt{t} (f_t - \E f_t,\ H_t)' \to^d N(0, S)
  \end{equation*}
  using the same argument as \citet{Wes:96}.
\end{proof}

@@

\begin{alem}\label{res:a1}
  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$. Then
  \begin{equation*}
    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
  \end{equation*}
\end{alem}

\begin{proof}
  We can rewrite this summation as
  \begin{multline*}
    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
    \ocltc{t} 2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue)
    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
  \end{multline*}
  Each of these individual summations can be shown to converge to
  zero in probability. First,
  \begin{equation*}
    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
    = O(R'/\sqrt{P}).
  \end{equation*}
  Also,
  \begin{align*}
    \Big\lvert \ocltc{t} &2 (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
    &\leq \ocltc{t} 2 \big\lvert (2 x_t'\btrue - y_{t+1} - \yh_{i,t+1}) x_t' \big\rvert
    \max_{t=R+1,\dots,R'} \lvert  \bh_t - \btrue \rvert \\
    & = O_p(R'/\sqrt{P})
  \end{align*}
  and
  \begin{equation*}
    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
    \leq \ocltc{t} \lvert x_t'x_t \rvert \max_{t=R+1,\dots,R'} (\bh_t - \btrue)'(\bh_t - \btrue)
    = O_p(R'/\sqrt{P}).
  \end{equation*}
  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
  construction, this completes the proof.
\end{proof}

\begin{alem}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and Assumptions~\ref{a1} -- \ref{a4}
  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
  \infty$ and $R' = o(\sqrt{P})$. Then
  \begin{enumerate}
  \item $\sup_{t=R'+1,\dots,T} | t^a H_t | \to^p 0$.
  \item $\sup_{t=R+1,\dots,R'} | t^a H_t | = O_p(1)$.
  \item $\sup_{t = R'+1,\dots,T} | t^a(\bh_t - \btrue) | \to^{p} 0$.
  \item $\sup_{t = R+1,\dots,R'} | t^a(\bh_t - \btrue) | = O_p(1)$.
  \end{enumerate}
\end{alem}

\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item The process $x_{t-1} \ep_t$ is $L_2$-NED of size $-1/2$ (on
    the same mixing process as the original variables) by
    Assumption~\ref{a3}, and the moment and size conditions in that
    assumption make it an $L_2$-mixingale of size $-1/2$ as well. The
    mixingale \fclt\ implies that, for any $t \to \infty$ as $T \to \infty$,
    \begin{equation}\label{eq:2}
      t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \to^d \lim (T^{1/2} / t^{1-a}) \cdot W(\lim t/T)
    \end{equation}
    where $W(\cdot)$ is a multivariate Gaussian process.

    If $t/T \to \gamma$ then $T^{1/2} / t^{1-a} \to 0$ and the limit
    in~\eqref{eq:2} is almost surely 0. If $t/T \to 0$, then
    \begin{equation*}
      \E\Big( t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big)^2 = t^{2a - 1}\, O(1)
    \end{equation*}
    and the limit in~\eqref{eq:2} is again almost surely 0. The
    Continuous Mapping Theorem then implies that
    \begin{equation*}
      \sup_{t=R'+1,\dots,T} \Big| t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s \Big| \to^p 0.
    \end{equation*}
  \item Again, $x_{t-1} \ep_t$ is an $L_2$-mixingale of size
    $-1/2$. As a result, we can use a maximal inequality of
    \cite{Mcl:75} (also available as Corollary 16.10 in
    \citealp{Dav:94}), giving
    \begin{align*}
      \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(t^{a - 1} \sum_{s=2}^t x_{s-1} \ep_s\Big)^2 \Big\rvert
      &\leq \E \Big\lvert \sup_{t=R+1,\dots,R'} \Big(\sum_{s=2}^t s^{a-1} x_{s-1} \ep_s\Big)^2 \Big\rvert \\
      &= O(1) \sum_{s=2}^{R'} s^{2a - 2}
    \end{align*}
    which converges to a finite limit.
  \item We have
    \begin{multline*}
      \sup_{t=R'+1,\dots,T} | t^a (\hat{\beta}_t - \btrue) | \leq \\
      \sup_{t,u =R'+1,\dots,T} \Big| [ \hat{B}_u - B]
      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R'+1,\dots,T} \Big|
      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|
    \end{multline*}
    and both terms converge to zero in probability by Part 1 and by
    assumption.
  \item Similar to the previous argument, we have
    \begin{multline*}
      \sup_{t=R+1,\dots,R'} | t^a (\hat{\beta}_t - \btrue) | \leq \\
      \sup_{t,u =R+1,\dots,R'} \Big| [ \hat{B}_u - B]
      t^{a-1} \sum_{s=2}^t x_s \ep_{s-1} \Big| + \sup_{t = R+1,\dots,R'} \Big|
      B t^{a-1} \sum_{2=1}^t x_s \ep_{s-1} \Big|.
    \end{multline*}
    Both terms are $O_p(1)$ by Part 2 and by assumption. \qedhere
  \end{enumerate}
\end{proof}

@@

\begin{proof}
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lvert \ocltb{t} (F_t - \E F_t) B \Big\rvert
  \sup_{t = R'+1,\dots,T} | H_t |.
\end{equation*}
From Lemma~\ref{res:a2}, $\sup_{t = R'+1,\dots,T} | H_t | \to^p 0$. The \clt\ implies
that $\ocltb{t} (F_t - \E F_t) = O_p(1)$,
establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
and~\eqref{eq:13} are similar.
\end{proof}

### 2014-10-31 mixedwindow.tex

% These commands are generated when the Monte Carlo and applied
% sections are run; I'm giving them definitions now so that LaTeX will
% compile the document even if that code hasn't been run yet.
\providecommand\bootsize{[missing]}
\providecommand\empiricalcriticalvalue{[missing]}
\providecommand\nboot{[missing]}
\providecommand\testsize{[missing]}
\providecommand\totalsims{[missing]}
\providecommand\windowlength{[missing]}
\providecommand\empiricaltable{[missing]}

@@

The next section presents our new statistics and Section~\ref{sec:2} presents
simulations that compare our test to \poscw\ original
statistics.  Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability and Section~\ref{sec:4} concludes. Proofs of
our results have been put in a separate Appendix along with
some minor supporting arguments \citep{Cal:14}.

@@

@@

>>>>

% These commands are generated when the Monte Carlo and applied
% sections are run; I'm giving them definitions now so that LaTeX will
% compile the document even if that code hasn't been run yet.
\providecommand\bootsize{[missing]}
\providecommand\empiricalcriticalvalue{[missing]}
\providecommand\nboot{[missing]}
\providecommand\nmod{[missing]}
\providecommand\testsize{[missing]}
\providecommand\totalsims{[missing]}
\providecommand\windowlength{[missing]}
\providecommand\empiricaltable{[missing]}
\providecommand\empiricaldraws{[missing]}
\providecommand\naivecriticalvalue{[missing]}

@@

The next section presents our new statistic. Section~\ref{sec:2} presents
simulations that compare our pairwise \oos\ test to \poscw\ original
statistics. Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability and Section~\ref{sec:4} concludes. Proofs of
our results have been put in a separate Appendix along with
some minor supporting arguments \citep{Cal:14}.

@@

Asymptotic normality of the OOS average follows directly from the
previous three assumptions without any other conditions. The proof is
presented in the Appendix and follows \citet{Wes:96} directly.

@@

Null hypothesis: $y_{t+1} - x_t'\beta_0$ is an MDS with respect to
\begin{equation*}
  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
\end{equation*}

Clearly, the main use of this theorem is to test the null hypothesis
$\E f_t = 0$.
